Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-13 mplr-2021/main.tex
Add examples for interactions

The implementation stores these observations as entities called
\texttt{interactions}. They are used for translating, modifying, and
aggregating Jalangi's raw event information to get an application-specific data representation. Each function invocation is stored as a \texttt{FunctionContainer} which contains an \texttt{ArgumentContainer} for each argument. Each \texttt{ArgumentContainer} contains the name and index of the argument and a collection of \texttt{interactions}. The interaction \texttt{getField} gets triggered whenever a property of an object gets accessed and it tracks the name of the accessed field. The invocation of an object's method is tracked with the \texttt{methodCall} interaction. The \texttt{usedAsArgument} interaction gets triggered when an argument is used in the invocation of a function. The \texttt{followingInteractions} property is used for inferring nested interfaces. It is an array that recursively records \texttt{interactions} on the return value of \texttt{getField} or \texttt{methodCall}.

>>>>

The implementation stores these observations as entities called
\texttt{interactions}. They are used for translating, modifying, and
aggregating Jalangi's raw event information to get an application-specific data representation. Each function invocation is stored as
a \texttt{FunctionContainer} which contains an \texttt{ArgumentContainer} for each argument. Each \texttt{ArgumentContainer} contains 
the name and index of the argument and a collection of \texttt{interactions}. As shown in \figref{fig:example-get-field-interaction}, the interaction \texttt{getField} gets triggered whenever 
a property of an object gets accessed and it tracks the name of the accessed field and the type of the returned value. The invocation of an object's method is tracked with 
the \texttt{methodCall} interaction. The \texttt{followingInteractions} property is used for inferring nested interfaces.
It is an array that recursively records \texttt{interactions} on the return value of \texttt{getField} or 
\texttt{methodCall}. \figref{fig:example-method-call-interaction} provides an example for both the \texttt{methodCall} interaction
and the \texttt{followingInteractions} property. Finally, the \texttt{usedAsArgument} interaction
gets triggered when an argument is used in the invocation of a function.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[t]{0.48\linewidth}
    \begin{lstlisting}[language=JavaScript,numbers=none]
function foo(hello) {
  if (hello.world) {
    // ...
  }
}

foo({ world: "..." });
    \end{lstlisting}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\linewidth}
    \begin{lstlisting}[language=JavaScript,numbers=none,escapechar=!]
{
  functionId_1: {
    //...
    functionName: 'foo',
    args: {
      0: {
        //...
        argumentName: "hello",
        interactions: [
          // ...
          !\textbf{\{}!
            !\textbf{code: "getField",}!
            !\textbf{field: "world",}!
            !\textbf{followingInteractions: [],}!
            !\textbf{returnTypeOf: "string",}!
          !\textbf{\},}!
        ],
      },
    },
  },
}
    \end{lstlisting}
  \end{subfigure}
  \caption{
      Example code that for \texttt{getField} interaction
    }
  \label{fig:example-get-field-interaction}
\end{figure*}

\begin{figure*}[t]
  \begin{subfigure}[t]{0.48\linewidth}
      \begin{lstlisting}[language=JavaScript,numbers=none]
function foo(bar) {
  if (bar.hello().world) {
    // ...
  }
}

foo({
  hello: function () {
    return {
      world: "xxx",
    };
  },
});    
      \end{lstlisting}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\linewidth}
      \begin{lstlisting}[language=JavaScript,numbers=none,escapechar=!]
{
  functionId_1: {
    //...
    functionName: "foo",
    args: {
      0: {
        // ...
        argumentName: "bar",
        interactions: [
          // ...
          !\textbf{\{}!
            !\textbf{code: "methodCall",}!
            !\textbf{methodName: "hello",}!
            !\textbf{functionId: "functionId\_2",}!
            !\textbf{followingInteractions: [}!
              !\textbf{\{}!
                !\textbf{code: "getField",}!
                !\textbf{field: "world",}!
                !\textbf{followingInteractions: [],}!
                !\textbf{returnTypeOf: "string",}!
              !\textbf{\},}!
            !\textbf{],}!
          !\textbf{\},}!
        ],
      },
    },
  },
}        
      \end{lstlisting}
    \end{subfigure}
  \caption{Example code for \texttt{}{methodCall} and \texttt{followingInteractions}}
  \label{fig:example-method-call-interaction}
  \end{figure*}
